Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-13 manuscript/manuscript.Rmd
fix table references

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
bibliography:
  - references.bib
  - GermanPolishpaper.bib
---

@@

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure S1A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100%) was 89% for crowd forecasts and 140% for the renewal model (Table SX). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure 3). Overall, low variance in forecast performance was closely linked with good mean performance (Figures 1AX and 1DX), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure XX), as well as the highest standard deviation of WIS values (relative WIS sd 154% a the two weeks ahead horizon), while the ensemble of crowd forecasts  (rel. WIS sd 76%) and the Hub ensemble (= 100%) showed more stable performance.

To varying degrees, all models exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened. For example, all models failed to predict the change in trend from increase to decrease that happened in early November... in Germany and severely overshot (Figure 2XX). This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past  of observations. The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so. Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle (www.dw.com) n.d.) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest. In December, cases rose again in Germany, with all models under-predicting this growth to varying extents. As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas. The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November. In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.

All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure 1X and 1X). Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts. This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure 1X) and only showed a small increase in uncertainty across forecast horizons. In spite of good performance in terms of the absolute error (Figure 1X), excessive sharpness led to forecasts which were severely overconfident (covering only 36% and 55% of observations with their 50% and 90% prediction intervals at a two week horizon, and only 5% and 38% four weeks ahead) (Figure 1X and Table SXX). Despite worse performance in terms of absolute error (Figure 1X), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.

The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons. The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure 1X). Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figure X and Table X), implying that over-prediction (e.g. when missing a peak) tended to be more costly in terms of the WIS.

Generally, trends in overall performance were broadly similar across locations (Figure XX).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure XXA, XXG).

@@

For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure 1A, Figure S1A). Relative WIS values for the models two weeks ahead were 122% (convolution model), 126% (crowd forecast), 100% (Hub ensemble) and 179% (renewal model). The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure 1A, Figure S1A), and also better than the convolution model three and four weeks ahead. Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate Rt trace from deaths, is not well suited for the task. The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure 1A, Table SX).

@@

Death forecasts, generally, showed greater coverage of the 50% and 90% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts. The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons. Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure 1X and XX). As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest. The convolution model was relatively sharp for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.

For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict. The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons. The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction. For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure XX).

@@

Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias. In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on December 28 2020 over the Christmas period) and a maximum of 10. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively. An overview of all models and ensemble verisons is shown in Table \@ref(tab:table-ensemble-versions) in the SI.

For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel. WIS 90% two weeks ahead). Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel. WIS 102% three weeks ahead, 106% four weeks ahead). The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects. Only for four week ahead predictions would removing the renewal model have improved performance (Table XX).

For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel. WIS of the hub-ensemble-realised 101% two weeks ahead, 105% four weeks ahead). Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons). This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Table XX) and especially worse for longer horizons.

We also considered the impact of our contributions on the mean, rather than the median ensemble. 
<!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (REFERENCE FIGURE). This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far. For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more ‘robust’ to changes than the mean ensemble. However, the ensemble version with all our forecasts included (“hub-ensemble-with-all”) tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or ‘safer’ for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.

@@

The good performance of crowd forecasts we found is in line with results from Farrow et al. who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants. The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models. However, this probably explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers. Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time. This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data). The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure XX), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention. Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output. We can therefore make no conclusive statements about the direct effects of researchers tuning their models, rather than create a new forecast from a naive baseline.

@@

```{r}
add_caption <- function(table, caption) {
  table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
                replacement = paste0("begin\\{table\\}[!h]\n\\\\caption\\{",
                                     caption,
                                     "\\\\\\\\\\\\hspace{\\\\textwidth}\\}\n"),
                x = table)
  return(table)
}
```

@@

```{r score-table-2}
table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
add_caption(table, caption)
```

@@

```{r score-table-4}
table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
add_caption(table, caption)

@@

```{r score-table-ensemble-4}
table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
add_caption(table, caption)
```

>>>>

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
bibliography:
  - references.bib
  - GermanPolishpaper.bib
---

@@

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \@ref(fig:agg-performance-all)A) and locations (Figure \@ref(fig:performance-locations-rel)A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100%) was 89% for crowd forecasts and 140% for the renewal model (Table \@ref(tab:score-table-2)). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \@ref(fig:distribution-scores)). Overall, low variance in forecast performance was closely linked with good mean performance (Figures \@ref(fig:agg-performance-all)H and and \@ref(fig:agg-performance-all)A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \@ref(fig:distribution-scores), as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts  (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

To varying degrees, all models exhibited trend-following behaviour and were rarely able to predict a change in trend before it had happened. For example, all models failed to predict the change in trend from increase to decrease that happened in early November... in Germany and severely overshot (Figure \@ref(fig:forecasts-and-truth)A). This was most striking for the renewal model, which extrapolated unconstrained exponential growth based on the recent past  of observations. The Hub ensemble and the crowd forecast, which had both been under-predicting throughout October, also failed to predict the change in trend after cases peaked, but less severely so. Human forecasters, possibly aware of the semi-lockdown announced on November 2nd 2020 (Deutsche Welle (www.dw.com) n.d.) and the change in the testing regime (with stricter test criteria) on November 11th 2020 (Ärzteblatt 2020), were fastest to adapt to the new trend, and the Hub ensemble slowest. In December, cases rose again in Germany, with all models under-predicting this growth to varying extents. As in October, the renewal model captured the phase of exponential growth in cases slightly better than other approaches, but again overshot when reported case numbers fell over Christmas. The large variance in predictions in January in Germany (severe under-prediction followed by severe over-prediction) may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. Similar trends in performance were evident in Poland, with the crowd forecast quickest at adapting to the change in trend in November. In general, there were fewer large outlier forecasts in Poland and in particular the renewal model performed more in line with other forecasts there.

All forecasting approaches, including the Hub ensemble, were overconfident and showed lower than nominal coverage (meaning that 50% (90%) prediction intervals generally covered less than 50% (90%) of the actually observed values) (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D). Coverage for all forecasts deteriorated with increasing forecast horizon, indicating that all forecasting approaches struggled to quantify uncertainty appropriately for case forecasts. This was especially an issue for crowd forecasts, which were markedly sharper (i.e., narrower) than other approaches (Figure \@ref(fig:agg-performance-all)E) and only showed a small increase in uncertainty across forecast horizons. In spite of good performance in terms of the absolute error (Figure \@ref(fig:agg-performance-all)G), excessive sharpness led to forecasts which were severely overconfident (covering only 36% and 55% of observations with their 50% and 90% prediction intervals at a two week horizon, and only 5% and 38% four weeks ahead) (Figure \@ref(fig:agg-performance-all)C,D and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)). Despite worse performance in terms of absolute error (Figure \@ref(fig:agg-performance-all)G), the renewal model achieved better calibration (comparable to the Hub ensemble), as uncertainty increased rapidly and non-linearly across forecast horizons.

The renewal model exhibited a noticeable tendency towards over-predicting reported cases across all horizons. The crowd forecast tended to over-predict at longer forecast horizons, whereas the Hub ensemble showed no systematic bias (Figure \@ref(fig:agg-performance-all)F). Regardless of a general relative tendency to over-predict, all forecasting approaches incurred larger absolute penalties from over- than from under-prediction (see decomposition of the WIS into absolute penalties for over-prediction, under-prediction and dispersion in Figures \@ref(fig:agg-performance-all)A and \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2) and \@ref(tab:score-table-4)), implying that over-prediction (e.g. when missing a peak) tended to be more costly in terms of the WIS.

Generally, trends in overall performance were broadly similar across locations (Figures \@ref(fig:performance-locations) and \@ref(fig:performance-locations-rel)).
Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly. However, relative to the Hub ensemble, the crowd forecasts performed noticeably better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure \@ref(fig:performance-locations-rel)A and \@ref(fig:performance-locations-rel)G).

@@

For deaths, the Hub ensemble outperformed the crowd forecasts as well as our model-based approaches across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B). Relative WIS values for the models two weeks ahead were 1.22 (convolution model), 1.26 (crowd forecast), 1 (Hub ensemble) and 1.79 (renewal model). The crowd forecasts performed better than the renewal model across all forecast horizons and locations (Figure \@ref(fig:agg-performance-all)B, Figure \@ref(fig:performance-locations)B), and also better than the convolution model three and four weeks ahead. Poor performance of the renewal model, especially at longer horizons, indicates that an approach that does not know about past cases, but instead estimates and projects a separate $R_t$ trace from deaths, is not well suited for the task. The convolution model was able to outperform both the renewal model and the crowd forecasts at shorter forecast horizons (where the delay between cases and deaths means that future deaths are largely informed by present cases), but saw performance deteriorate at three and four weeks ahead (where case predictions from the renewal model were increasingly used to inform death predictions) (Figure \@ref(fig:agg-performance-all)B, Table \@ref(tab:score-table-4)).

@@

Death forecasts, generally, showed greater coverage of the 50% and 90% prediction intervals than case forecasts and no decrease in coverage across forecast horizons, indicating that it might be easier to appropriately quantify uncertainty for death forecasts. The Hub ensemble had the greatest coverage, with empirical coverage of the 50% and 90% prediction intervals exceeding 50%, and 90%, respectively, across all forecast horizons. Coverage for the crowd forecasts and our model-based approaches was generally lower than that of the Hub ensemble and mostly slightly lower than nominal coverage (Figure \@ref(fig:agg-performance-all)C and \@ref(fig:agg-performance-all)D). As for cases, the crowd forecast tended to be the sharpest and uncertainty increased most slowly across forecast horizons, and the renewal model forecasts generally were widest. The convolution model was relatively sharp for short forecast horizons, but had rapidly (and non-linearly) increasing uncertainty for longer forecast horizons, driven by increasing uncertainty in the underlying case forecasts.

For deaths, the ensemble of crowd forecasts had a consistent tendency to over-predict \@ref(fig:agg-performance-all)F. The convolution model had a strong tendency to under-predict, which steadily decreased for longer forecast horizons. The renewal model (which over-predicted for cases) and the Hub ensemble slightly tended towards under-prediction. For deaths, absolute over- and under-prediction penalties were more in line with a general relative tendency to over- or under-predict than for cases (Figure \@ref(fig:agg-performance-all)A, \@ref(fig:agg-performance-all)B and Tables \@ref(tab:score-table-2), \@ref(tab:score-table-4)).

@@

Of our three models, only the renewal model and the crowd forecast were included in the official Forecast Hub median ensemble (“hub-ensemble-realised”), while the convolution model was never included as it was deemed too similar to the existing renewal model, thus potentially introducing bias. In the official Hub ensemble, there were on average 7.1 models included (including our own), with a median of 7, a minimum of 4 (on December 28 2020 over the Christmas period) and a maximum of 10. Versions that included either all of our models (“hub-ensemble-with-all”) or only one of them (“hub-ensemble-with-X”) were computed retrospectively. An overview of all models and ensemble versions is shown in Table \@ref(tab:table-ensemble-versions) in the SI.

For cases, our contributions (compared to the Hub ensemble without our contributions) consistently improved performance across all forecasting horizons (rel. WIS 0.9 two weeks ahead, Table \@ref(tab:score-table-ensemble-2)). Contributions from the crowd forecasts alone also were positive across all forecast horizons, while contributions from the renewal model became negative for longer horizons (rel. WIS 1.02 three weeks ahead, 1.06 four weeks ahead). The realised ensemble including both models performed better or equal compared to all versions with only one model included for up to three weeks ahead, suggesting synergistic effects. Only for four week ahead predictions would removing the renewal model have improved performance (Table \@ref(tab:score-table-ensemble-4)).

For deaths, contributions from the renewal model and crowd forecast together improved performance only for one week ahead predictions and showed an increasingly negative impact on performance for longer horizons (rel. WIS of the hub-ensemble-realised 1.01 two weeks ahead, 1.05 four weeks ahead, Tables \@ref(tab:score-table-ensemble-2) and \@ref(tab:score-table-ensemble-4)). Individual contributions from both the renewal model and the crowd forecast were largely negative, while a version of the Hub ensemble with only the convolution model included would have performed consistently better across all forecast horizons (with the positive impact increasing for longer horizons). This is especially interesting as the convolution model performed consistently worse than the pre-existing Hub ensemble (Figure \@ref(fig:agg-performance-all)) and especially worse for longer horizons.

We also considered the impact of our contributions on the mean, rather than the median ensemble. 
<!-- In general, the median ensemble tended to perform slightly better than the mean ensemble - needs more analysis -->
General trends were similar, with the notable exception of the convolution model, which had a consistently positive impact on the median ensemble, but a mixed and mostly slightly negative impact on the mean ensemble (Figures \@ref(fig:agg-performance-ensemble)B and \@ref(fig:agg-performance-ensemble-mean)B). This may happen if a model is more correct directionally relative to the pre-existing ensemble, but overshoots in absolute terms, thereby moving the ensemble too far. For both the mean and the median ensemble, changes in performance from adding or removing models were of a similar order of magnitude, suggesting that at least in this instance, with a relatively small ensemble size, the median ensemble was not necessarily more ‘robust’ to changes than the mean ensemble. However, the ensemble version with all our forecasts included (“hub-ensemble-with-all”) tended to perform relatively better for the median ensemble than the mean ensemble, suggesting that adding more models may be more beneficial or ‘safer’ for the median than for the mean ensemble as directional errors can more easily cancel out than errors in absolute terms.

@@

The good performance of crowd forecasts we found is in line with results from Farrow et al. who also report strong performance of human predictions in past Flu challenges despite difficulties to recruit a large number of participants. The advantage of crowd forecasts we observed over our semi-mechanistic models is likely in part explained by the fact that we compared an ensemble of crowd forecasts with single models. However, this probably explains only part of the difference and performance relative to the Hub ensemble strongly suggests that human insight is valuable when predicting highly volatile and hard-to-predict quantities such as case numbers. Relatively good performance of our semi-mechanistic models short-term, but not longer-term, suggests that model-based forecasts are helpful to extrapolate from current conditions, but require some form of human intervention or additional assumptions to inform forecasts when conditions change over time. This human intervention may be particularly important when dealing with artefacts in reporting and data anomalies (and especially when using daily, rather than weekly data). The large variance in predictions in January in Germany for example (severe under-prediction followed by severe over-prediction, see Figure \@ref(fig:forecasts-and-truth)A), may in part be caused by the fact that the renewal model operated on daily data and therefore was susceptible to fluctuations in daily reporting around Christmas that would not have influenced on weekly reporting. While we were not able to observe how expert opinion informed other models submitted to the Forecast Hub, conversations with the Hub organisers suggest that forecasts tended to benefit from a large degree of human intervention. Unfortunately, we were not able to test a scenario in which users were asked to alter an existing model output. We can therefore make no conclusive statements about the direct effects of researchers tuning their models, rather than create a new forecast from a naive baseline.

@@

```{r}
add_caption <- function(table, caption, label = NULL) {
  if (is.null(label)) {
    label <- paste0("tab:", opts_current$get("label"))
  }
  table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
                replacement = paste0("begin\\{table\\}[!h]\n", 
                                     "\\\\caption\\{",
                                     "\\\\\\label\\{", label, "\\}",
                                     caption,
                                     "\\\\\\\\\\\\hspace{\\\\textwidth}\\}\n"),
                x = table)
  return(table)
}

@@

```{r score-table-2}
table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
add_caption(table, caption, label = "tab:score-table-2")
```

@@

```{r score-table-4}
table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
add_caption(table, caption, label = "tab:score-table-4")

@@

```{r score-table-ensemble-4}
table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
add_caption(table, caption)
